Speed and strength of epidemic intervention

### 2019-07-24 doc/speedstrength.tex
working

\section{Results}

In this section, we use both strength- and speed-based decompositions to compare different intervention strategies for HIV. In particular, we compare how the amount of early vs. late transmission affect each intervention strategies.

In order to

>>>>

\section{Examples}

In this section, we use both strength- and speed-based decompositions to compare different intervention strategies for the Human immunodeficiency virus (HIV). 
These examples are not meant to provide precise or accurate estimates of the effectiveness of intervention strategies; 
instead, we use these examples to demonstrate how strength- and speed-based decompositions allow us to better evaluate each control strategy under different scenarios.
In particular, we study how the amount of early HIV transmission can affect our decisions.

We model the infection kernel of the HIV as a sum of two gamma distributions:
\begin{equation}
K(\tau) = \mathcal R \left(\tsub{p}{early} \tsub{f}{early}(\tau) + (1-\tsub{p}{early}) \tsub{f}{late}(\tau) \right).
\end{equation}
The first gamma distribution, $\tsub{f}{early}(\tau)$, models early HIV transmission during the acute infection stage.
We assume that $\tsub{f}{early}(\tau)$ has a mean of 3 months \citep{hollingsworth2008hiv} and a shape parameter of 3.
The second gamma distribution, $\tsub{f}{late}$, models HIV transmission during the asymptomatic stage and the disease stage (after progression to Acquired Immune Deficiency Syndrome (AIDS)).
We assume that $\tsub{f}{late}(\tau)$ has a mean of 10 years \citep{babiker2000time} and a shape parameter of 2 (this vaguely approximates the wide generation-interval distribution of the HIV \citep{fraser2004factors}).
Finally, $\tsub{p}{early}$ is the proportion of early HIV transmission.

As our baseline scenario, we assume that early transmission is responsible for 23\% of the total transmission \citep{hayes2006amplified}.
Based on the growth rate estimate ($0.452 \textrm{year}^{-1}$) from a HIV prevalence data in pregnant women in South Africa \citep{barron2013eliminating}, our baseline reproduction number is $3.17$.
Increasing the amount of early transmission reduces the mean generation time, which in turn decreases the reproduction number.

\begin{figure}
\includegraphics[width=\textwidth]{../figure/figure1.pdf}
\caption{This is not a figure.}
\end{figure}

\subsection{Univarsal testing and treatment}
